Designing Turk Experiments for Visual Statistical Inference

### 2013-06-10 paper_turk.tex
Abstract
abstract and introduction modified

It has been found that the visual statistical inference \cite{buja:2009}, which does not have distributional assumptions, has the power comparable to the conventional tests \cite{Majumder:2011}. To examine the power of visual statistical inference we recruited human subjects from Amazon Mechanical Turk \cite{turk} for evaluating lineups \cite{buja:2009, Majumder:2011}. The Turk website is designed to recruit workers for simple and easy tasks. Even though the task of evaluating lineups is easy, the technical design of the experiment is complex and the tools available to design this from Turk website is just too simple. In this paper we present an alternative way to conduct the survey by designing a separate web site and getting turk worker do their job from this web site. We also present the simulation experiment design to estimate the power of visual statistical inference.

@@

We have seen some advancement in visual statistical inference since it was first introduced by Buja \cite{buja:2009} where they have introduced formal methods for testing the significance of findings using lineup protocols. The power of visual statistical inference or lineup protocol is studied by Majumder \cite{Majumder:2011} and it is revealed that power could be as good as conventional test. But where the conventional test does not exists, visual inference could be only inferential procedure without compromising a lot in power. The effect of different graphical design while selecting visual test statistic is studied by Heike \cite{heike:2012}.

Even though under some situation it is possible to obtain the power of visual inference theoretically \cite{Majumder:2011},  it is hard to obtain power explicitly with a mathematical formula since it is very much dependent on individual observation. One approach to estimate the power is to recruit observers to evaluate lineups obtained in known controlled situation \cite{Majumder:2011}. It is better to get observers as diverse as possible without being much concerned about the observers formal training about statistical graphics.

Amazon Mechanical Turk web site \cite{turk} is a very good resource for recruiting reliable survey participants for visual experiments. The web site is very convenient and reliable to collect simple experiment data. But to design a complex experiment like what we need using their web interface is a pain and often a very time consuming work. So, to run the turk experiment we felt the necessity for a well customized web site where the lineups presented to the observers could be easily controlled according to the experimental design. The work flow design of such a mechanism is shown in figure \ref{fig:turk_work_flow}. The plan is to forward turk workers to a well customized web site while payment could be processed from turk web site. This facilitates getting data directly in a local server.

@@

>>>>

Human observers are needed to evaluate lineups that are used to test the significance of findings using statistical graphics. One good option is to recruit people from online workplace like Amazon Mechanical Turk (MTurk). It has the facilities to design online task that could serve the purpose of evaluation of lineups. But the MTurk website is designed to recruit workers for simple and easy tasks. Even though the task of evaluating lineups is easy, the technical design of the underlying experiment may be complex and the tools available to design this from MTurk website is just too simple. In this paper we present an alternative way to conduct the survey on lineups by designing a separate web site and getting turk worker do their job from this web site. The web site is now hosted and has been in use. Multiple experiments are already done through this web site. It turns out to be a very efficient way of getting lineups being evaluated by online observers. Getting results from this web site is very convenient and secure. This paper also describes how to design MTurk experiments to evaluate lineups.

@@

There have been some advancement in visual statistical inference since it was first introduced by Buja \cite{buja:2009} where they have proposed formal methods for testing the significance of findings using lineup protocols. The power of visual statistical inference or lineup protocol is studied by Majumder \cite{majumder:2013} and it is revealed that power could be as good as conventional test and some times even better. But where the conventional test does not exists, visual inference could be the only inferential procedure without compromising a lot in power.

In visual statistical inference the test statistics is a plot of the observed data. This plot is placed randomly in a layout of plots called lineup. The rest of the plots in the lineups are generated from the model specified by the null hypothesis. The lineup is evaluated by human observer. If the observed plot is identified in the lineup, the null hypothesis is rejected.

%The effect of different graphical design while selecting visual test statistic is studied by Heike \cite{heike:2012}.

Even though under some situation it is possible to obtain the power of visual inference theoretically \cite{Majumder:2011},  it is hard to obtain power explicitly with a mathematical formula since it is very much dependent on individual observation. One approach to estimate the power is to recruit observers to evaluate lineups obtained in known controlled situation \cite{majumder:2013}. It is better to get observers as diverse as possible without being much concerned about the observers' formal training about statistical graphics.

There are some reasons a researcher needs to evaluate a lineup. One is to assess the power of the visual test. The another reason would be to make decision based on the lineup. Other reasons could be to present the results of the conventional test with visual tools such as lineup.

\subsection{Amazon Mechanical Turk (MTurk)}

Amazon Mechanical Turk web site \cite{turk} is a very good resource for recruiting reliable survey participants for visual experiments. This is the place where people come to work online and get paid. The web site is very convenient and reliable to collect simple experiment data. But to design a complex experiment like what we need using their web interface is a pain and often a very time consuming work. So, to run the turk experiment we felt the necessity for a well customized web site where the lineups presented to the observers could be easily controlled according to the experimental design. The work flow design of such a mechanism is shown in figure \ref{fig:turk_work_flow}. The plan is to forward turk workers to a well customized web site while payment could be processed from turk web site. This facilitates getting data directly in a local server.

Figure \ref{fig:amazon_task} displays an example of such a task taken from their web site. In this task a worker just has to select from a pool of options and submit the task. The instructions are usually accompany the task and they are very simple and easy to follow.

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=5in]{amazon_task.pdf} 
   \caption{An example of amazon mechanical turk task. Tasks are usually very simple and designed for human evaluations. With each task, simple instructions are given for workers to follow. The workers first accept the task before submitting their response.}
   \label{fig:amazon_task}
\end{figure}

@@

\begin{table}[hbtp]
\caption{Amazon mechanical turk experiments and their properties. Duration in hours per 100 tasks show the popularity of some tasks compared to others.}
\centering
\begin{tabular}{rlrrrrrrr}
  \hline
& Experiment& \multicolumn{2}{c}{ Total Task}& Average & \multicolumn{2}{c}{Duration (hour)} & Payment & Pay rate\\
\cline{3-4} \cline{6-7}
Serial & description & submitted & rejected & time(min) & Actual & 100 task& \$/task & \$/hour\\ 
  \hline
1 & Boxplot & 406 & 106 & 10.68 & 146.48 & 36.08 & 0.50 & 2.81 \\ 
  2 & Scatterplot & 359 &   9 & 10.80 & 42.68 & 11.89 & 1.00 & 5.58 \\ 
  3 & Contaminated plot & 219 &  19 & 13.53 & 126.17 & 57.61 & 1.00 & 2.22 \\ 
  4 & Polar vs Cartesian & 110 &  10 & 20.65 & 11.65 & 10.59 & 1.00 & 2.91 \\ 
  5 & Hist vs density & 234 &  37 & 17.85 & 41.57 & 17.76 & 1.00 & 3.36 \\ 
  6 & Violin vs boxplot & 417 &  17 & 17.95 & 105.87 & 25.39 & 1.00 & 3.34 \\ 
  7 & Group separation & 106 &   6 & 16.13 & 5.15 & 4.86 & 1.00 & 3.72 \\ 
  8 & Sine Illusion & 101 &   1 & 16.52 & 78.38 & 77.60 & 1.00 & 3.63 \\ 
  9 & Gene expression & 103 &   3 & 12.47 & 11.27 & 10.94 & 0.50 & 2.41 \\ 
  10 & Test normality & 406 &   6 & 22.70 & 74.35 & 18.31 & 1.00 & 2.64 \\ 
   \hline
\end{tabular}
\label{tbl:mturk}
\end{table}

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=3in]{rejected_task.pdf}
      \includegraphics[width=3in]{task_duration.pdf} 
   \caption{Percentage of rejected tasks and duration of each experiment in hour per 100 tasks for each of the 10 experiments. Most of the tasks got rejected for box plot experiment.  Even though the sine illusion experiment took longest to finish the rejection rate is lowest for this experiment.}
   \label{fig:task_duration}
\end{figure}
